Tina Paper In Development

### 2024-10-09 docs/writing/paper.tex
Adding a little bit in functional limits

\subsection{Functional Limits}

>>>>

\subsection{Functional Limits}
With such high resolution, multiple logistics concerns arise. First is the file size. With such a high resolution, the size of the images can become extremely large. A cookie
5 inches in diameter would result in an image with 67,000 pixels squared. This easily exceeds the 2.5 GB maximum file size in a TIFF - most software for viewing the file will also 
be incompatible with any file this big as well.
